---
title: "ggugent: ggplot2 UGent theme"
author: Louis Lippens
date: "`r Sys.Date()`"
output: md_document
---

**Important.** This package is currently under development.

# ggugent

The `ggugent` package provides a custom, opinionated ggplot2 theme (`theme_ugent`) tailored to the branding guidelines of Ghent University (UGent). This theme allows R users to create ggplot2 visualisations that align with the university's style, including font, colours, and other aesthetic elements.

## Installation

You can install the development version from GitHub.

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("llippens/ggugent")
```

## Usage

After installation, you can use the `theme_ugent` function to apply the UGent theme to your ggplot2 objects. Here's an example using the `mtcars` dataset.

```{r, eval=FALSE}
library(ggplot2)
library(ggugent)
ggplot(data = mtcars, mapping = aes(x = wt, y = mpg)) +
  geom_point() +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    alpha = .15,
    colour = "#1E64C8"
  ) +
  facet_wrap(~cyl, ncol = 3) +
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) +
  scale_y_continuous(limits = c(5, 35)) +
  labs(
    title = "Motor Trend car road tests",
    subtitle = "Vehicles miles per gallon vs weight by number of cylinders",
    caption = "Source: Motor Trend US magazine",
    x = "Weight (x1,000 lbs)",
    y = "Miles / (US) gallon"
  ) +
  theme_ugent(
    base_size = 20,
    faculty_colour = "EB"
  )
```

## Features

1.  **Custom Font**. The theme uses 'UGent Panno Text' as the default font (and 'Arial' as secondary or fall-back font).
2.  **Adaptable Text Size**. The `base_size` parameter sets a standard font size from which relative sizes of other text elements are calculated.
3.  **UGent Colour Theme**. The theme uses UGent blue `#1E64C8` as its base colour.
4.  **Faculty Colours**. The `faculty_colour` parameter specifies faculty colours through character shortcodes like "EB" for the Faculty of Economics and Business Administration.
    - `LW` for the Faculty of Arts and Philosophy (orange, `#F1A42B`)
    - `RE` for the Faculty of Law and Criminology (warm red, `#DC4E28`)
    - `WE` for the Faculty of Sciences (aqua, `#2D8CA8`)
    - `GE` for the Faculty of Medicine and Health Sciences (salmon pink, `#E85E71`)
    - `EA` for the Faculty of Engineering and Architecture (medium sky-blue, `#8BBEE8`)
    - `EB` for the Faculty of Economics and Business Administration (light green, `#AEB050`)
    - `DI` for the Faculty of Veterinary Medicine (purple, `#825491`)
    - `PP` for the Faculty of Psychology and Educational Sciences (warm orange, `#FB7E3A`)
    - `BW` for the Faculty of Bioscience Engineering (turquoise, `#27ABAD`)
    - `FW` for the Faculty of Pharmaceutical Sciences (light purple, `#BE5190`)
    - `PS` for the Faculty of Political and Social Sciences (green, `#71A860`)

## Contributing

Contributions are appreciated! The development of this package is still in its very early phase. If you would like to contribute, please use a pull request. Issue reports are also warmly welcomed.

## Licensing

The code in this project is licensed under MIT license. See [LICENSE](LICENSE) for more information.
